Framing Effects in the Wild

### 2023-04-13 pres/Presentation.Rmd
prepare Job Talk

.footnote[(Very liberal after Sniderman and Theriault 2004)]

@@

## What is necessary for the study of framing effects?

# 1. Precisely identifiable, sharp change of frames in communication.
# 2. Good measure of frames in mind.

@@

- **Clearly identifiable short-term-change** in migration coverage.
- Clear expectations regarding impact.
- Change not debated in the media $\rightarrow$__No co-treatment__! <font size="5" color="#004A95"> `r Citep(myBib["Spirig2020"])`</font>.

@@

# How does this affect migration attitudes?

## Theoretical Expectations

![](vis/CognitiveStorage.png)

### Increased exposure to crime frames will lead to...
- H1: **more conservative** attitudes towards migration.
- H2: **stronger association** of crime and migration attitudes.

@@

- Collected 2.5M news articles from major German daily newspapers' websites.
- Two-step identification of crime frames:
  1. **Select migration content**:
    + Generate dictionary, oversample migration content.
    + Annotate 1800 articles.
    + Supervised deep-learning model (BERT) to **identify migration content**.
  2. **Select crime frames**.
    + Same, but subset of articles about migration content.

@@

TreatmentTrendPlot(size = 2, 
                   dpa_corrected = T) +
  theme_xaringan()

@@

German Longitudinal Election Study (GLES) Panel <font size="5" color="#004A95"> `r Citep(myBib["GLES2017Panel"])`</font>.

## Frames in Mind (continued)

@@

>>>>

.footnote[(Very freely after Sniderman and Theriault 2004)]

@@

@@

- **Clearly identifiable short-term-change** in migration coverage.
- Clear expectations regarding impact (more conservative migration attitudes).
- Change not debated in the media $\rightarrow$__No co-treatment__! <font size="5" color="#004A95"> `r Citep(myBib["Spirig2020"])`</font>.

@@

<!-- class: inverse, center, middle -->

<!-- # How does this affect migration attitudes? -->

<!-- --- -->

<!-- ## Theoretical Expectations -->

<!-- .pull-left[ -->

<!-- ![](vis/CognitiveStorage.png) -->

<!-- ] -->

<!-- .pull-right[ -->

<!-- ### Increased exposure to crime frames will lead to... -->
<!-- - H1: **more conservative** attitudes towards migration. -->
<!-- - H2: **stronger association** of crime and migration attitudes. -->

<!-- ] -->

<!-- --- -->

@@

- Collected 2.5M news articles from major German daily newspapers' websites.
- Two-step identification of crime frames:
  1. **Select migration content**:
    + Generate dictionary, oversample migration content.
    + Annotate 1800 articles.
    + Supervised deep-learning model (BERT) to **identify migration content**.
  2. **Select crime frames**.
    + Same procedure.
    + Estimation of crime content **within** migration content.

@@

TreatmentTrendPlot(size = 2, dpa_corrected = F, palette = c("red", "#004A95")) +
  theme_xaringan()

@@

### German Longitudinal Election Study (GLES) Panel <font size="5" color="#004A95"> `r Citep(myBib["GLES2017Panel"])`</font>.

**Questions on:**

- [Immigration Attitudes]()
- [Integration Attitudes]()
- [Crime Attitudes]()
- [Support for RR]()
- [Most Important Problem]()

@@

# Appendix

## Operationalization DV

## Operationalization DV (continued)
